Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2019-11-03 index.Rmd

---
title: "Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis"
author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
date: "`r Sys.Date()`"
output:
  bookdown::html_book:
    theme: united
---

@@

When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?

How has the first sign of powdery mildew changed over the seasons and between experimental sites?

How has the first sign of powdery mildew changed over the seasons and between experimental sites?

When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop?

Do infections that occur before flowering increase the probable yield loss?

What is the length of a mungbean season and how has it varied in this trial?
   - This data has not been collected or is not accurate enough to be useful to answer this question.

@@

Variability among host genotypes and probable influence of season given that over the years, the genotype studied changed from Berken, Crystal to Jade.

>>>>

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
date: "`r Sys.Date()`"
output:
  bookdown::html_book:
    theme: united
---

@@

+ When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?

+ How has the first sign of powdery mildew changed over the seasons and between experimental sites?

+ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?

+ Do infections that occur before flowering increase the probable yield loss?

+ What is the length of a mungbean season and how has it varied in this trial?  
   - This data has not been collected or is not accurate enough to be useful to answer this question.

@@

+ Variability among host genotypes.  
   + The probable influence of season might be influenced by host genotype. This is because newer varieties were adopted into experimental trials as they were released.  
   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.

+ Estimations of plant maturity stages over each growing season. These estimations might able to be computed using APSIM.
